\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2015-01-07 draft010515.tex
convert top p.1 ex_ante to text; input to draft

\vskip.2in
\subsubsection{Strong Bindings}
When there is perfect external enforcement of an agreement that specifies the exact tariff each government must adhere to, \Textcite{bs2005} derive the result that the optimal rigid, strong binding $\tau_S^R$ will be set at the level that is politically efficient for the expected realization of political pressure, $\ga(s)$. In their environment, $\ga(s)$ is exogenously determined and so the optimal trade agreement tariff is chosen as
\[
  \tau_S^R = \frac{4\left[\expect \ga(s) - 1\right]}{25 - 4\expect \ga(s)}
\]
which is simply Equation~\ref{eq:eff} evaluated at the expected $\ga$.

@@

>>>>

\vskip.2in
\subsubsection{Strong Bindings}
\label{sec:strong}
When there is perfect external enforcement of an agreement that specifies the exact tariff each government must adhere to, \Textcite{bs2005} derive the result that the optimal rigid, strong binding $\tau_S^R$ will be set at the level that is politically efficient for the expected realization of political pressure, $\ga(s)$. In their environment, $\ga(s)$ is exogenously determined and so the optimal trade agreement tariff is chosen as
\[
  \tau_S^R = \frac{4\left[\expect \ga(s) - 1\right]}{25 - 4\expect \ga(s)}
\]
which is simply Equation~\ref{eq:eff} evaluated at the expected $\ga$.

@@

\section{Ex-Ante Lobbying}
\label{sec:exante}

\input{ex_ante}

### 2015-01-07 ex_ante.tex
convert top p.1 ex_ante to text; input to draft

\documentclass[12pt]{article}

\addtolength{\textwidth}{1.4in}
\addtolength{\oddsidemargin}{-.7in} %left margin
\addtolength{\evensidemargin}{-.7in}
\setlength{\textheight}{8.5in}
\setlength{\topmargin}{0.0in}
\setlength{\headsep}{0.0in}
\setlength{\headheight}{0.0in}
\setlength{\footskip}{.5in}
\renewcommand{\baselinestretch}{1.0}
\setlength{\parindent}{0pt}
\linespread{1.1}

\usepackage{amssymb, amsmath, amsthm, bm}
\usepackage{graphicx,csquotes,verbatim}
\usepackage[backend=biber,block=space,style=authoryear]{biblatex}
\setlength{\bibitemsep}{\baselineskip}
\usepackage[american]{babel}
%dell laptop
\addbibresource{C:/Users/Kristy/Dropbox/Research/xBibs/tradeagreements.bib}
%\addbibresource{C:/Users/Kristy/Documents/Dropbox/Research/xBibs/tradeagreements.bib}
\renewcommand{\newunitpunct}{,}
\renewbibmacro{in:}{}

\DeclareMathOperator*{\argmax}{arg\,max}
\usepackage{xcolor}
\hbadness=10000

\newcommand{\ve}{\varepsilon}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}
\newcommand{\ta}{\theta}
\newcommand{\al}{\alpha}
\newcommand{\Ta}{\Theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\btn}{\bm{\tau^n}}
\newcommand{\ga}{\gamma}
\newcommand{\Ga}{\Gamma}
\newcommand{\de}{\delta}

\begin{document}
\begin{center}
Ex-ante Lobbying
\end{center}
%\chead{Klimenko, Ramey and Watson (2007) summary.tex}

\vskip.2in
Ex-ante lobbying is lobbying before the trade agreement is signed to affect the level at which TA will be set (this also impacts what will be possible ex-post)
\begin{itemize}
	\item ex-post lobbying is lobbying after the TA is signed to change the applied tariff (to be clear, can also affect the incentives of the government in setting the TA)
	\item lobby may have to pay both times, depending on whether the TA takes the form of an exact tariff commitment or a tariff cap
		\begin{itemize}
			\item As in Section [ ], when facing exact tariff commitment lobby's optimal ex-post effort choice is zero. However, when facing a tariff cap, protection will only be supplied if lobby exerts effort (i.e. according to $\tau^N(\ga(e)) = \frac{8\ga(e) - 5}{68 - 8 \ga(e)} = \tau^R_{W,e}$).
			\item So ex-ante lobbying adds a second time at which the lobby may have an incentive to exert effort in the case of a tariff cap, a first time in the case of an exact commitment
		\end{itemize}
	\item For simplicity, adding ex-ante lobbying in case of endogenous lobbying ONLY
\end{itemize}

\vskip.5in
BS2005 set up that this paper follows holds that governments set TA so that TA will be at optimal level ex-post: gov't will be able to set the applied tariff that matches the political pressure it experiences at the time, and it tunes the TA so that it's exactly the amount of pressure it wants
\begin{itemize}
	\item There is no possibility of ex-ante lobbying in BS2005 framework, so have to figure out what it means
	\item What welfare does each party get at TA stage?
		\begin{itemize}
			\item For lobby is very clear: lobby just knows that this will bind its future action: so paying earlier only matters insofar as it improves ex-post profits
			\item For govts: compare to BS2005, which is all forward looking. With ex-ante, government might get/lose political capital from different interested parties if lobbying is strong enough to outweigh future concerns; otherwise, it's all forward looking---what will future gains and losses be
		\end{itemize}

@@

\end{document}

>>>>

%\documentclass[12pt]{article}

%\addtolength{\textwidth}{1.4in}
%\addtolength{\oddsidemargin}{-.7in} %left margin
%\addtolength{\evensidemargin}{-.7in}
%\setlength{\textheight}{8.5in}
%\setlength{\topmargin}{0.0in}
%\setlength{\headsep}{0.0in}
%\setlength{\headheight}{0.0in}
%\setlength{\footskip}{.5in}
%\renewcommand{\baselinestretch}{1.0}
%\setlength{\parindent}{0pt}
%\linespread{1.1}

%\usepackage{amssymb, amsmath, amsthm, bm}
%\usepackage{graphicx,csquotes,verbatim}
%\usepackage[backend=biber,block=space,style=authoryear]{biblatex}
%\setlength{\bibitemsep}{\baselineskip}
%\usepackage[american]{babel}
%dell laptop
%\addbibresource{C:/Users/Kristy/Dropbox/Research/xBibs/tradeagreements.bib}
%\addbibresource{C:/Users/Kristy/Documents/Dropbox/Research/xBibs/tradeagreements.bib}
%\renewcommand{\newunitpunct}{,}
%\renewbibmacro{in:}{}

%\DeclareMathOperator*{\argmax}{arg\,max}
%\usepackage{xcolor}
%\hbadness=10000

%\newcommand{\ve}{\varepsilon}
%\newcommand{\ov}{\overline}
%\newcommand{\un}{\underline}
%\newcommand{\al}{\alpha}
%\newcommand{\expect}{\mathbb{E}}
%\newcommand{\ga}{\gamma}
%\newcommand{\Ga}{\Gamma}
%\newcommand{\de}{\delta}

%\begin{document}

In many situations, it is realistic to assume that, in addition to the ex-post lobbying examined throughout this text, lobbying also takes place before the trade agreement is signed to affect the terms of the trade agreement. To reiterate what has been shown in previous sections, although ex-post lobbying occurs after the trade agreement is signed in order to impact the level of the applied tariff, it alters the incentives of governments when they negotiate the trade agreement. Similarly, ex-ante lobbying is aimed directly at changing the level of the trade agreement tariff, but here lobbies only engage in this activity in order to alter what will be possible ex-post.

With the addition of the possibility of ex-ante lobbying, the lobby may have to pay twice. As in Section~\ref{sec:strong}, when facing a trade agreement in which commitments take the form of strong bindings, the lobby's optimal ex-post effort choice is zero. However, when facing a tariff cap, protection will only be supplied at the ex-post stage if the lobby exerts effort. Thus, ex-ante lobbying adds a second time at which the lobby may have an incentive to exert effort in the case of a tariff cap; it introduces a first time at which the lobby may supply non-zero effort in the case of a strong binding.

\vskip.5in
For simplicity, adding ex-ante lobbying in case of endogenous lobbying ONLY

BS2005 set up that this paper follows holds that governments set TA so that TA will be at optimal level ex-post: gov't will be able to set the applied tariff that matches the political pressure it experiences at the time, and it tunes the TA so that it's exactly the amount of pressure it wants
\begin{itemize}
	\item There is no possibility of ex-ante lobbying in BS2005 framework, so have to figure out what it means
	\item What welfare does each party get at TA stage?
		\begin{itemize}
			\item For lobby is very clear: lobby just knows that this will bind its future action: so paying earlier only matters insofar as it improves ex-post profits
			\item For govts: compare to BS2005, which is all forward looking. With ex-ante, government might get/lose political capital from different interested parties if lobbying is strong enough to outweigh future concerns; otherwise, it's all forward looking---what will future gains and losses be
		\end{itemize}

@@

%\end{document}
